Cosmic web correlations with the shape, spin and peculiar velocties of dark matter halos

### 2013-11-06 paper/main.tex
first words on spin alignment

{\bf Contreras et al. (2014)} & V-Web & $1 \hMpc$ & 
filament &$?$ & $>10^{12}$\hMsun\\

&   & & 
filament &$?$ & $<10^{12}$\hMsun\\

&   & & 
wall & $?$ & all masses\\\hline

{\bf Contreras et al. (2014)} & Vp-Web & $1 \hMpc$ & 
filament &$?$ & $>10^{12}$\hMsun\\

&   & & 
filament &$?$ & $<10^{12}$\hMsun\\

&   & & 
wall & $?$ & all masses\\\hline

@@

@@

\newpage
\subsection{Angular Momentum Alignment}

\begin{figure*}
\includegraphics[width=0.80\textwidth]{Fig3.pdf}
\caption{Median of $\cos\theta$ quantifying the angular momentum
  alingment for the Vweb (left) and the Tweb (right) at two different
  grid resolutions. In the upper (lower)  panels the angle $\theta$ is
  measured between the first (third) eivenvector and the angular
  momentum vector.} 
\end{figure*}

>>>>

{\bf Contreras et al. (2014)} & T-Web & $0.5-1 \hMpc$ & 
filament &none & $<10^{12}$\hMsun\\

&   & & 
filament & - & $>10^{12}$\hMsun\\

&   & & 
wall & none & $<10^{12}$\hMsun\\

&   & & 
wall & - & $>10^{12}$\hMsun\\\hline

{\bf Contreras et al. (2014)} & Vp-Web & $0.5-1 \hMpc$ & 
filament &none & $<10^{12}$\hMsun\\

&   & & 
filament & none & $>10^{12}$\hMsun\\

&   & & 
wall & none & $<10^{12}$\hMsun\\

&   & & 
wall & + & $>10^{12}$\hMsun\\\hline

@@

\subsection{Angular Momentum Alignment}

\begin{figure*}
\includegraphics[width=0.80\textwidth]{Fig3.pdf}
\caption{Median of $\cos\theta$ quantifying the angular momentum
  alingment for the Vweb (left) and the Tweb (right) at two different
  grid resolutions. In the upper (lower)  panels the angle $\theta$ is
  measured between the first (third) eivenvector and the angular
  momentum vector.
  \label{fig:spin_alignment}
} 
\end{figure*}

We now take a look at the alignment of the halo spin with the cosmic
web. This characterization is done in terms of the angle between the
angular momentum vector and the first/third eigenvector.

Figure \ref{fig:spin_alignnment} shows the results as a function of
the halo mass. In the case of the V-web the trends can be summarized
as follows. Low mass halos $10^{12}$\hMsun do not show any
preferential alignment with the cosmic web. Halos more massive than
this threshold have their spin slightly perpendicular to the
direction defined by the first eigenvector (defining sheets) and
uncorrelated to the third eigenvector (filament direction). This
translates into a weak tendency for the spin to lie on the
sheet-plane.

In the case of the T-web there is a similar trend for low mass halos
$10^{12}$\hMsun not to have any preferential direction with respect to
the cosmic web. High mass halos present a weak alignment with the
first eigen vector and anti-alignment with the third
eigenvector. Summarizing, the spin of massive halos tends to be
slightly perpendicular to filaments and sheets.

@@
